Bayesian Evidence Synthesis:Opioid Crisis

### 2020-04-27 Rcodes/JAGS_overdoses.Rmd
figures lastly added

```{r}
MCMCtrace(test)
```

```{r}
plot(test)
```

```{r get the samples of N and show a distribution}
pst_mtx.N = as.matrix(test)
head(pst_mtx.N)
N <- pst_mtx.N[,1]
length(N)
```

```{r}
ggplot(data = as.data.frame(N), aes(x= N)) +geom_histogram()+ geom_vline(xintercept =10000)
```

>>>>

```{r}
MCMCtrace(test) 
# better than #plot(test)
```

```{r get the samples of N and show a distribution}
pst_mtx.N = as.matrix(test)
head(pst_mtx.N)
N <- pst_mtx.N[,1]
head(N)
length(N)
```

hist(N)
```

## get the $O_t$, $U_t$, $x_{A,t}$ ommitted for now.

### 2020-04-27 latex/researchpaper.tex
figures lastly added

Posterior samples of $O_t$ was accurate as before.

\subsubsection{Posterior Predictive Check}
\iffalse
could vary over time or it can be staritified for a better realization of the reality. The survey size could also vary such as $n_{A}=100$ or $n_{A}=10000$ in later examples. 
\fi

@@

 nevertheless, the bayesian generative model is 
\bibliographystyle{alpha}
\bibliography{sample.bib}
\end{document}

>>>>

\begin{figure}[h]
	\centering
	\includegraphics[width=1\linewidth]{Figures/hist_N.png}
	\caption{Boxplot of posterior samples of $N$ (20000 samples for each month)}
	\label{hist_unk_n}
\end{figure}

Posterior samples of $O_t$ was accurate as before. [mention that although the mixing was not possible with the maximum capacity of the computer, at least the proper prior seems to help a lot for the estimation of $O_t$ which depends on the N. ][put the figure and briefly explain that the the estimation for the variable is not hugely affected.]
\begin{figure}[h]
	\centering
	\includegraphics[width=1\linewidth]{Figures/unknown_N_ot.png}
	\caption{Boxplot of posterior samples of $O_t$ (20000 samples for each month) with simulated $O_t$ values as red dots.}
	\label{pst_ot_unk_n}
\end{figure}

[put the figures and briefly explain that the the estimation for the variables are not hugely affected.]
\begin{figure}[htb]
	\centering
	\subfloat[ppc of $U_t$]{\includegraphics[width=.50\columnwidth]{Figures/unk_N_ppc1_ut.png}\label{ppc_ut_unk_n}}
	\subfloat[ppc of $x_{A,t}$]{\includegraphics[width=.50\columnwidth]{unk_N_ppc1_xt}\label{ppc_xt_unk_n}}
	\caption[Initial result: box plots of predictive posterior samples of $U_t$ and $x_{A,t}$]{Boxplots of posterior predictive samples of $U_t$ and $x_{A,t}$ (1000 samples) with the actual data point of simulated $U_t$,$x_{A,t}$ value. The simulated values are shown as a red dots.}

\iffalse
could vary over time or it can be staritified for a better realization of the reality. The survey size could also vary such as $n_{A}=100$ or $n_{A}=10000$ in later examples. 
\fi

@@

\bibliographystyle{alpha}
\bibliography{sample.bib}
\end{document}
